\documentclass[10pt]{report}
\usepackage{vmargin}
\newcommand{\SicoreAddress}{\textsc{Damon Sicore} \\ 1117 W. Jefferson Street\\ Waxahachie, TX 75165}
\thispagestyle{empty}
\author{Damon Sicore}
\title{Damon Sicore}
\setmarginsrb{1in}{1in}{1in}{1.4in}{0pt}{0mm}{0pt}{0mm}
\begin{document}
\begin{center}
\LARGE Damon Sicore \\
\normalsize
1117 W. Jefferson Street \\
Waxahachie TX, TX 75165 \\
512-963-5126\\
\texttt{damon@sicore.com}\\
\texttt{https://damon.sicore.com}\\
\end{center}

\subsection*{ACHIEVEMENTS:}  Produced 30 major releases of Firefox;
World-record holder for \emph{Most Software Downloaded in a Single Day} for
Firefox 4; Est.  Number of Users impacted: 5 billion people;  Deployed
one-billion Wikipedia instances on mobile devices in China in 2016; Built
Mozilla engineering from 18 engineers to over 600;  Formed teams and efforts
and created \emph{Firefox for Android}, the \emph{Rust Programming Language,
WebGL, FirefoxOS, WebAssembly}, and \emph{Mozilla Research}.  Formed
performance team at Wikimedia and \emph{doubled the performance of Wikipedia
for the world}; Eliminated all Critical Security Bugs in Firefox.  Successfully
launched two cryptocurrencies: NEAR and Aleo which now have a combined market
cap of over 16 billion USD.

\subsection*{CURRENT POSITION:}

\subsubsection*{MONADIC.US -- \texttt{https://monadic.us}. -- \emph{2016 to
Present. }} \emph{CEO} -- MONADIC.US is a professional services company
providing expert Rust compiler and cryptography services.  Our main product is
\texttt{snarkOps}, a suite of tools to enable rapid development of
zero-knowledge applications on decentralized networks.  MONADIC.US is a core
validator of the Aleo network, and our tools enabled Aleo to successfully
launch their programmable zero-knowledge decentralized network with a current
market cap of 6 billion USD.


\subsection*{EXPERIENCE:}

\subsubsection*{Aleo, Inc. -- \emph{January, 2021 to March, 2022. }} \emph{Vice
President of Engineering} -- Responsible for the development of the Aleo
zero-knowledge cryptographic decentralized ledger engineering project.
Responsible for Engineering and IT/Operations.  \texttt{https://aleo.org}

\subsubsection*{NEAR Protocol, Inc. -- \emph{January, 2020 to December 2020. }}
\emph{Vice President of Engineering} -- Responsible for the development of the
NEAR Protocol decentralized ledger engineering project. Responsible for
Infrastructure, Open Finance, and Ecosystem Engineering.
\texttt{https://near.org}

\subsubsection*{Wikimedia Foundation, San Francisco, CA. -- \emph{February 2015
to July 2015. }} \emph{Vice President of Engineering, Head of Product--}
Promoted to Head of Product in addition to VP of Engineering.  Responsible for
the editing, reading, and mobile software product direction and planning for
Wikimedia (Wikipedia and supporting projects).

\subsubsection*{Wikimedia Foundation, San Francisco, CA. -- \emph{September
2014 to February 2015. }} \emph{Vice President of Engineering--} Responsible
for Wikipedia Engineering, a team of 160 engineers developing the software,
infrastructure, security, IT/Ops, Fundraising tech, and QA for Wikipedia.

\subsubsection*{Edmodo, Inc., San Mateo, CA. -- \emph{March 2013 to June 2014.
}} \emph{Vice President of Engineering--} Responsible for the engineering,
security, IT/Ops, Support, and QA of Edmodo, an education and school-based
social network with over 18 million users.

\subsubsection*{Mozilla Corporation, Mountain View, CA. -- \emph{November 2010
to February 2013. }} \emph{Vice President of Engineering--} Built and led a
team of over 600 open source software engineers, technical leads, managers, and
directors developing the Firefox Web browser, the Mozilla open source platform,
Firefox for Android, and FirefoxOS.  Firefox has almost half a billion daily
users, and my mission is to ensure choice and innovation--pushing the Web
forward--by creating the best browser in the world.

\subsubsection*{Mozilla Corporation, Mountain View, CA. -- \emph{January 2007
to November 2010. }} \emph{Sr. Director of Platform Engineering--} Joined
Mozilla as a director in 2007 to lead a team 22 engineers.  Expanded platform
engineering to over 75 open source software engineers, technical leads, and
managers to develop the Mozilla platform, consisting of several foundational
subsystems on which many products are developed (e.g., Firefox, SeaMonkey,
Thunderbird, etc.).  Oversaw four teams, each with managers reporting directly
to me:  JavaScript, Layout, Content, and Graphics as well as contractors and
direct reports.  Responsible for driving releases, organizational development
and structure, overall goal-setting, scheduling, management, hiring, and
compensation activities for the Mozilla platform team.  Most notable
achievements so far is driving the platform for Firefox 3, 3.5, and 3.6 which
is used by hundreds of millions of users on a daily basis.  Drove the platform
for Firefox 4.0, a major version of Firefox.


\subsubsection*{JBoss, Inc., Austin, TX. -- \emph{December 2004 to January
2007, }} \emph{Lead of JBoss Labs and Development Manager.}

% Responsible for JBoss
%Labs as well as lead of the open source projects: JBoss Wiki and Shotoku.  JBoss
%Labs is the community site for all JBoss projects and is a complete open source
%hosting facility;  JBoss Labs consists of portal framework and a complete
%revision control system using Subversion, JBoss Portal 2.2, JBoss Wiki, Shotoku,
%and JBoss Forum integrations to host open source projects.  Additional duties
%include:

\subsection*{PROFESSIONAL KNOWLEDGE:}
\begin{description}


\item{\emph{Leadership Knowledge:}} Experienced executive capable of leading
all aspects of a company especially engineering and product management.
Organizational Development, Management Systems and Control (Project
Management), Software Configuration Managment, Organizational Behavior, Human
Resource Management, and the Management Process.  Professional leadership
consultant and mentor.

\item{\emph{Primary Knowledge:}} Programming Languages, Logic and Functional
Programming, Decentralized Computing, Cryptography and Zero-knowledge,
Distributed Development Methodologies: Agile, Extreme Programming, etc.,
Operating Systems, Networks, and Software Engineering, Organizational Behavior,
and Leadership.

\item{\emph{Additional Knowledge:}} Cryptography and digital security
(encryption technologies), Embedded systems, peer-to-peer agents, blockchain
theory and applications, JBoss AS Applied Architectures, System Administration
(router and firewall configuration, Sendmail, ipchains, DNS/bind, Tripwire,
Linux kernel, bash, sed, awk, backup and recovery, Samba, NFS, LDAP,
PGP/gnupg, clustering and load-balancing, and general TCP/IP networking).

\item{\emph{Language Knowledge:}} Rust, JavaScript, Python, Ada, Java 15 yr.,
C++ 6 yr., C 8 yr.  Pascal, Lisp, Fortran, Motorola 680x0 Assembly, IBM 370
Assembly, Numerous markup languages like HTML, SQL and PL/SQL.

\item{\emph{Teaching and Training:}} Professional Instructor of JBoss
Application Server Advanced J2EE classes, and J2EE System Administration using
JBoss.  Instructor for Revision Control using Subversion classes.

\item{\emph{Specialized Technologies:}} All Java and J2EE Technologies:  EJB3
(and 2.0)  JSP, JMS, Transactions, JDBC, XML, JNDI, Servlets (Resin, JRun,
JServ, Jakarta-Tomcat), AOP (Aspect Oriented Programming), XDoclet and
attribute-oriented programming, CORBA (Visigenic, Orbix, and Sun
implementations).

\item{\emph{Enterprise Servers:}} JBoss Application Server (used professionally
since inception), JBoss Portal 2.x, Weblogic Application Servers,  Weblogic
Personalization/Commerce Server 3.51, Weblogic (5.1.0 and 4.5.1), ATG Dynamo,
SilverStream, WebSphere, Orion.


\item{\emph{Operating Systems Knowledge:}} UNIX (Linux, Darwin, Embedded Linux,
FreeBSD, OpenBSD, Solaris, AIX, and HPUX), OS X,  Windows XP/2K/NT/95, OS/2,
Novell Netware, Vax/VMS, VM, Stratus VOS, MS-DOS.

\item{\emph{Databases:}} NoSQL, Oracle, DB2 (Universal DB), PostgreSQL, MySQL,
MS SQLServer, Sybase, and various embedded databases.

\item{\emph{UML and Object-oriented Tools:}} TogetherJ (Control Center and
Together), Rational Rose.

\item{\emph{Webservers:}} Apache and iPlanet.

\item{\emph{Special Purpose Hardware/Software:}} gcc, make, ANT, Visual C++,
Subversion, CVS, Visual Source Safe, PVCS, XWindow, Apriori, \TeX, \LaTeX.
Maven.


\end{description}

%
%\begin{itemize}
%
%	\item Professional Instructor for JBoss Advanced J2EE Development and
%	Administration Training classes at corporations and public trainings and
%	around the world.
%
%	\item Travel and give speeches about cutting edge Java technologies and the
%	Open Source development methodology.
%
%	\item Write articles about JBoss and other open source technologies and
%	projects.
%
%	\item Produce video and audio podcasts to help open source projects
%	communicate ideas in the community
%
%	\item Manage resources and duties of developers living around the world,
%	working on JBoss Labs and other JBoss projects.
%
%	\item Task creation, tracking, and actual development duties.
%
%	\item Change management duties such as creation of policies and best practices
%	for JBoss.
%
%	\item Developed JBoss' svn code repository branching policies.
%
%	\item Develop J2EE applications for JBoss Labs and JBoss Portal.
%
%	\item Track and monitor all JBoss Open Source projects using metrics developed
%	in JBoss Labs.
%
%\end{itemize}


\subsection*{EXPERIENCE, CONT.:}

\subsubsection*{Transplace, Inc., Plano, TX. -- \emph{December 2002 to December
2004, }} 
    \emph{Director of Change Management.} 
%
%Responsible for establishing
%Change Management practices for all Transplace development.

%\begin{itemize}
%
%	\item Specified and implemented revision control and code promotion policies
%	and procedures.
%
%	\item Trained 45+ developers in Subversion and revision control concepts.
%
%	\item System administration of all change managments systems (Solaris,
%	FreeBSD, and Linux).
%
%\end{itemize}
%
%Additional responsibilities included being the resident JBoss and J2EE
%application server systems expert working with individual developers to help
%them expand their skill sets.
%
%\subsubsection*{Ipseity Consulting, LLC. -- \emph{August 2000 to December 2002}}
%
%	\begin{description}
%
%		\item{\bf{\emph{Software Architect--}}} Created a company providing software
%		architecture, design, and programming for companies in need of immediate
%		senior Internet software architecture knowledge and experience.   Services
%		range from complete Java distributed computing and enterprise-wide
%		architectures to small consumer-oriented embedded devices.  Projects
%		include:
%
%    	\begin{list}{-}{}
%
%			\item{\emph{Transplace, Inc., Plano, TX, Consulting Software Architect--}}
%			Hired as JBoss expert in order to support production, test, and
%			development JBoss deployments at Transplace.  Transplace has over 15
%			instances of JBoss and my duties included:
%
%			\begin{itemize}
%
%				\item Ensuring that all JBoss deployments are standardized and use best practices.
%
%				\item Instruct developers on the best development and deployment techniques using JBoss.
%
%				\item Enable the use of JBoss AS Clustering in the enterprise.
%
%				\item Deliver a build mechanism utilizing XDoclet in order to reduce
%				developer time spent writing J2EE interfaces.
%
%			\end{itemize}
%
%			\item{\emph{Alliance Data Systems, Inc. Dallas, TX, Consulting Software
%			Architect--}}  Responsible for leading the ADS development team to design
%			and implement their Customer Service Representative, Account Reporting,
%			and Fees Processing applications using a J2EE architecture. Additionally,
%			Rearchitected entire existing code base to be a solid multi-tiered J2EE
%			system, to utilize a standard build system, and to implement
%			attribute-oriented programming.  Utilized the following components:
%
%			\begin{itemize}
%
%				\item{JBoss General Architecture, ver. 3.2.1 --} Integrated JBoss with
%				existing BEA Weblogic and mainframe applications in order to replace BEA
%				with JBoss.
%
%				\item{Tomcat J2EE Web Applications --}  All applications were built to
%				the latest Sun Web application specs and bundled accordingly.
%
%				\item{DB2 and Oracle Databases --}  Integrated primary and data
%				warehouse databases to provide sophisticated reporting application.
%				Live data on an OS/390 mainframe, while warehoused data was stored in
%				Oracle.
%
%				\item{XDoclets --}  Implemented attribute-oriented programming to reduce
%				writing of repetitive code and streamline development processes.
%
%			\end{itemize}
%
%			Additionally provided networking and application security services as a
%			Unix system administration and security expert, and implemented their bug
%			tracking processes using Bugzilla
%
%			\item{\emph{Sony Music New Technologies, Inc. San Francisco, CA,
%			Consulting Software Architect--}}  Assisted Sony to build their Affinity
%			Platform.
%
%			\item{\emph{Tacit Knowledge Systems, Inc. Palo Alto, CA, Consulting
%			Software Architect--}}  Assisted in porting Tacit Knowlege Systems'
%			application (Expertise Services Platform) to Oracle from SQLServer.
%
%			\item{\emph{Consulting Software Architect--}}  Worked with various
%			corporate development teams to provide senior and immediate experience to
%			their development efforts.  Projects included:
%
%			\begin{itemize}
%
%				\item{JBoss Open Source EJB Server Applications--} Message driven EJB
%				architectures for remote client data distribution and transaction
%				processing.
%
%				\item{Weblogic 5.1--} EJB backend architecture for managing
%				transactions.
%
%				\item{Resin JSP--} Servlet/JSP infrastructures.
%
%				\item{Oracle 8i}
%
%				\item{PostgreSQL--}Database for transactions.
%
%				\item{Swing GUI Client front ends for server configuration and
%				monitoring}
%
%				\item{Together Control Center--}Complete design/documentation of entire
%				architectures.
%
%			\end{itemize}
%
%			In addition to authoring applications, services included:
%
%			\begin{itemize}
%
%				\item Network and application level security consulting services,
%
%				\item Unix system administration services,
%
%				\item Integration and support services.
%
%			\end{itemize}
%
%		\end{list}
%
%	\end{description}
%

  \subsubsection*{Creditland.com -- \emph{August 1999 to August 2000}}
    \emph{Sr. Software Architect.}

%  \begin{description}
%
%    \item{\bf{\emph{Sr. Software Architect--}}} Designed and implemented an EJB
%    solution as the core foundation of Creditland's Web site.  Created the  site
%    using WebLogic 4.5.1 on Solaris as the JSP (load-balanced with  Apache),
%    Servlet, and EJB server driving Oracle 8.0.5 and 8i databases.   Created the
%    architecture from start to finish as a complete implementation  of
%    Creditland's Web site.  Architected and implemented the decisioning
%    interface between Creditland's  application server and the proprietary
%    decisioning engine via a unique  Enterprise Java Bean solution.  Team lead
%    on the project and responsible  for peer reviews and development
%    methodologies.  Other key technologies on which I focus include:
%
%    	\begin{list}{-}{}
%
%    		\item Load balancing techniques for farmed Web servers;
%
%    		\item XML generation for data interchange;
%
%    		\item Web caching techniques using the latest hardware and software;
%
%    		\item Business to business Internet interfaces;
%
%    		\item Transaction management between farmed and clustered application
%    		servers;
%
%    		\item Client/server code design and optimization to boost
%    		application/site performance to its maximum in a distributed
%    		environment.
%
%    	\end{list}
%
% \end{description}
%
  \subsubsection*{Deloitte \& Touche Consulting, DRT Systems --\emph{March 1999
  to August 1999}}
    \emph{Consultant.}

%	\begin{description}
%
%    \item{\bf{\emph{Consultant--}}} Joined the Distributed Computing Practice
%    with DRT Systems.
%
%    \item{\bf{\emph{Technical Manager, Business Process Outsourcing Project
%    --}}}  Managed team of nine software engineers to architect solutions for
%    Web-based business processes for a major life insurance company.  Projects
%    include an automated underwriting engine implemented using a Java CORBA
%    distributed solution, assessing an Enterprise Java Bean underwriting
%    solution, commission statements presented on the Web for remote agents using
%    Java Servlets pulling from Oracle databases, and business automation using
%    NeuronData's Elements Advisor rules engine to streamline workflow. Solutions
%    provided were engineered in a heterogeneous environment consisting of
%    Solaris, NT, AS/400, Oracle, Novell, OS/2, and proprietary imaging systems.
%    Goals include providing a complete Java and Sun solution for new business
%    processes on the Web.
%
%    \item{\bf{\emph{SilverStream Load Balancing and Security --}}} Participated
%    in a focused  study of the SilverStream application server's load balancing,
%    failover,  and security capabilities.
%
%  \end{description}
%
  \subsubsection*{ADAC Healthcare Information Systems -- \emph{June 1996 to
  March 1999}}
    \emph{Sr. Software Engineer.}
%
%  \begin{description}
%
%    \item{\bf{\emph{Sr. Software Engineer -- }}} Design, documentation, and
%    coding of Java applications using Oracle databases via CORBA and JDBC as a
%    client/server solution for a radiology information system. Object oriented
%    development tools include: Rational Rose for Java, Visual Cafe Professional
%    2.5, Visual C++ 5.0, and Visual J++.  Software packages also include the use
%    of Visigenic VisiBroker 3.2 and Weblogic dbKona, all versions of JDK, Swing,
%    and JFC, and Visual Basic.  Projects include development of Java-to-native
%    code network communication through CORBA and JNI, C++, DLLs, GUI interfaces,
%    and business model/rules design and coding with thorough documentation.
%    Application focuses on Web-enabled solution for physicians to access an
%    Oracle database and send transactions to external devices/systems such as
%    email/fax/printing and interfaces with other healthcare information systems.
%
%    \item{\bf{\emph{DIN-PACS: Digital Imaging Network: Picture Archiving and
%    Communications System --}}} PowerPACS Worklists are the central feature of
%    ADAC's DIN-PACS solution. The worklists are used to manage the work within
%    the radiology department and provide metrics for the radiology department to
%    allow more efficient operation.  The worklists are integrated into the RIS,
%    the Quality Control Imaging Workstations and Diagnostic Imaging Workstations
%    via a C++ to Java CORBA interface which I developed to access an Oracle
%    database via JDBC.
%
%    \item{\bf{\emph{Interface Software Engineer --}}} Design, engineering, and
%    implementation of network interfaces between client/server applications,
%    databases (Oracle), and remote systems in the healthcare arena.
%    Object-oriented programming and C programming on various platforms.  Project
%    utilized the CAI Interface Engine/Integrated Development Environment (TDM)
%    for the development of TCP/IP communications between UNIX (HP, DEC, AIX,
%    SunOS, SCO), Windows NT, and Windows95 operating systems.  Incorporated Java
%    into existing client/server applications and interfaces.  Previous projects:
%    HL7 Interfaces, Installations, and Interface Support.
%
%  \end{description}
%
\subsection*{CERTIFICATIONS:}
Sun Certified Programmer for the Java 2 Platform.

\subsection*{EDUCATION:}
Texas A\&M University \\
College Station, TX \\
Bachelor of Computer Science with a minor in Management. \\
May 1996 \\

References Available Upon Request.

\end{document}
